DATA 612 Week #1 Textbook Exercises

### 2019-09-04 DATA621/Week 1 Textbook Exercises.Rmd
Wrapped up work on week 1 textbook exercises

sat <- read.delim("data/sat.txt") 
```

@@

>>>>

sat <- read.delim("data/sat.txt")

temp <- sat %>%
  summarise(mpg = list(enframe(quantile(total, probs=c(0.25, 0.5, 0.75))))) %>% 
  unnest() %>%
  spread(name, value)

sat %>%
  summarise(`Min.` = min(total),
            Mean = mean(total),
            `Max.` = max(total),
            Count = n()) %>%
  merge(temp) %>%
  select(`Min.`, `25%`, `50%`, Mean, `75%`, `Max.`, Count) %>%
  kable() %>%
  kable_styling()
```

@@

**There are a couple of things that have a similar spike.  For example military personnel per 1000...**

```{r}
ggplot(divusa, aes(x = year)) +
  geom_line(aes(y = divorce, color = "Divorce")) +
  geom_line(aes(y = military, color = "Military")) + 
  scale_y_continuous(sec.axis = sec_axis(~.*1, name = "Per 1,000 People"))+ 
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Per 1,000 Women", x = element_blank(), color = element_blank()) +
  theme(legend.position = "bottom") +
  ggtitle("Divorce and Military Personnel Rate")
```

**...the marriage rate...**

```{r}
ggplot(divusa, aes(x = year)) +
  geom_line(aes(y = divorce, color = "Divorce Rate")) +
  geom_line(aes(y = marriage, color = "Marriage")) +
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Per 1,000 Women", x = element_blank(), color = element_blank()) +
  theme(legend.position = "bottom") +
  ggtitle("Divorce and Marriage Rate")
```

**...and most strikingly, the female labor force participation rate.**

```{r}
ggplot(divusa, aes(x = year)) +
  geom_line(aes(y = divorce, color = "Divorce Rate")) +
  geom_line(aes(y = femlab, color = "Female Labor Force Participation")) +
  scale_y_continuous(sec.axis = sec_axis(~.*1, name = "Percent of Working Age Females"))+ 
  scale_colour_manual(values = c("blue", "red")) +
  labs(y = "Per 1,000 Women", x = element_blank(), color = element_blank()) +
  theme(legend.position = "bottom") +
  ggtitle("Divorce Rate and Female Labor Force Participation")
```
